---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
number_sections: true

vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#sequence tree or sequence names
First thing the software needs is the sequence files and sequence names. 
```{r get inputs}
library(synal)
library(Biostrings)
specNames <- c('Scer','Spar','Smik','Skud','Sbay','Sarb')
filename <- system.file('examples','exampleAlignment.fa',package='synal')
aln <- readDNAStringSet(filename)

```


#proto-gene sequence

After you read the alignment file and sequence names, the ORF of interest should be given. If you are interested in an S.cerevisiae annotated ORF, you can find the sequence using findYgeneSeq function.
```{r findYgeneSeq}

ygene <- findYGeneSeq('YBR196C-A')
```

#alignment and getting subalignments
After giving correct inputs, it is easy to get subalignments and Amino acid translations.

```{r subalignment}
  dnalist <- align(aln,'YBR196C-A',ygeneSeq = ygene)
  DNAStr <- dnalist$dnaAlignmentList[[1]]
  start <- dnalist$dnaAlignmentList[[2]]
  stop <- dnalist$dnaAlignmentList[[3]]
  subalignment <- subseq(DNAStr,start,stop)
  aa_alignment <- dnalist$aa_alignment
```

#finding orthologs
if you are interested in finding all overllaping ORFs with your ORF of interest you can do so.
```{r find orthologs}
types<-specNames#c('scer','Spar','Smik','Skud','Sbay','Sarb')
vec <- c(1,1,1,0,0,0)
types <- types[vec>0]
homologs <- findHomolog(DNAStr[vec>0], start, stop, ygene, types, orfName = 'YBR196C-A')
homologs
```

#getting dataframe
todo:add example inputs to use in analyze function
```{r analysis}
#dataTable <- analyze('../../synal_deneme/','YBR013C',types)
```

#all in one
finally all of the above can be done using a single function for all the sequences in the given alignment file

```{r all in one, warning=FALSE}
#dataTable <- alignAnalyze('~/Downloads/combined/YBR013C/YBR013C_alignment.fa','YBR013C',outputDirectory = '../../synal_deneme/',specNames = specNames)
```
